---
title: "COTASS Interpersonal Violence Project - Risk Factors for Experiencing Interpersonal Violence"
author: "Filip Kaleta"
date: "2023-12-06"
output: 
  html_document:
    toc: true
---

# Packages

```{r include=FALSE}
library(haven)
library(psych)
library(ggplot2)
library(scales)
library(stringr)
library(dplyr)
library(forcats)
library(tidyverse)
library(labelled)
library(car)
library(miceadds)
library(texreg)
library(sandwich)
library(broom)
library(knitr)
library(foreign)

```

# Objects of Variables

```{r include=FALSE}
rm(list=ls())

df <- read_dta("IPV-and-depression3.dta")

View(df)

df <- df[!(df$whichcotass == 1 | df$whichcotass == 2),]

head(df)

var_label(df$sex_c1c2)
val_labels(df$sex_c1c2)

var_label(df$c1_war1)
val_labels(df$c1_war1)

var_label(df$c1_war2)
var_label(df$c1_war3)
var_label(df$c1_war4)
var_label(df$c1_war5)
var_label(df$c1_war6)
var_label(df$c1_war7)
var_label(df$c1_war8)

var_label(df$ethnicity)
val_labels(df$ethnicity)

var_label(df$ethn_minority)
val_labels(df$ethn_minority)


#demographic

sex <- df$sex_c1c2
age <- df$age_yrs
marstat <- df$marstat
ethnicity <- df$ethnicity
ethn_minority <- df$ethn_minority

val_labels(df$tenure)
tenure <- df$tenure
table(tenure)

val_labels(df$hq1_housetype)
val_labels(df$hq2_roomsforsleep)
val_labels(df$hq3_floorqual)
val_labels(df$hq4_roofqual)
val_labels(df$hq5_wallqual)
val_labels(df$hq6_lighting)
val_labels(df$hq7_cookfuel)
val_labels(df$hq8_watersource)
val_labels(df$hq9_toilet)

housing1 <- df$hq1_housetype #0 = good, 1 = poor
housing2 <- df$hq2_roomsforsleep #0 = good, 1 = poor
housing3 <- df$hq3_floorqual #0 = good, 1 = poor
housing4 <- df$hq4_roofqual #0 = good, 1 = poor
housing5 <- df$hq5_wallqual #0 = good, 1 = poor
housing6 <- df$hq6_lighting #0 = good, 1 = poor
housing7 <- df$hq7_cookfuel #0 = good, 1 = poor
housing8 <- df$hq8_watersource #0 = tap within premises, 1 = tap outside, 2 = other (NEEDS TRANSFORMATION?)
df$hq8_watersource_bin <- ifelse(df$hq8_watersource > 0, 1, 0) # recoded; bin = binary
housing8_bin <- df$hq8_watersource_bin 
housing9 <- df$hq9_toilet #0 = good, 1 = poor

appliances.count <- df$el_count

#Questions asked about whether household owns X vehicle
tr_any <- df$tr_any
tr_bike <- df$tr_bike
tr_car_van <- df$tr_car_van
tr_mbike <- df$tr_mbike
tr_trac_bus_other <- df$tr_trac_bus_oth
tr_count <- df$tr_count

education <- df$education #0-5 = no education to university or higher; 6 = other (6 NEEDS REMOVING?)

fin_strain <- df$finstrain #0 = comfortably, 4 = v diff to make ends meet

#war
war.combatant <- df$c1_war1
war.injured <- df$c1_war2
war.lost.fam <- df$c1_war3
war.close.fam.injured <- df$c1_war4
war.lost.other <- df$c1_war5
war.other.injured <- df$c1_war6
war.displaced <- df$c1_war7
war.lost.property <- df$c1_war8

#tsunami
tsu1 <- df$c1_tsu1
tsu2 <- df$c1_tsu2
tsu3 <- df$c1_tsu3
tsu4 <- df$c1_tsu4
tsu5 <- df$c1_tsu5
tsu6 <- df$c1_tsu6
tsu7 <- df$c1_tsu7
tsu8 <- df$c1_tsu8
tsu9 <- df$c1_tsu9
tsu10 <- df$c1_tsu10 #qual q

#Depression 
bdi <- df$pbecktot

var_label(df$depscreen)
var_label(df$depscreeni)
table(df$depscreen) #0 = the diagnosis is indeterminate, because questions have missing data, 1 = diagnosis is negative, 5 = diagnosis is positive
table(df$depscreeni) #same as above but additionally, 3 = criteria for diagnosis are positive except for exclusion criteria

cidi_diagnosis1 <- df$depscreen
cidi_diagnosis2 <- df$depscreeni

#SI
var_label(df$beck_q9)
val_labels(df$beck_q9)
table(df$beck_q9)
bdi.si <- df$beck_q9

var_label(df$e18_i)
var_label(df$e18_ii)
var_label(df$e19_i)
var_label(df$e19_ii)
var_label(df$e20_i)
var_label(df$e20_ii)

table(df$e18_i) #probably this one because count v low in e18_ii
table(df$e18_ii)

table(df$e19_i) 
table(df$e19_ii)

table(df$e19a_i) #only if 19 'yes'
table(df$e19a_ii)


cidi_si_thoughts_death <- df$e18_i
cidi_si <- df$e19_i
cidi_si_plans <- df$e19a_i

#SSH

var_label(df$e20_i) #only asked if SI present (pos on e19)
table(df$e20_i)

ssh <- df$e20_i

#Interpersonal Violence

head(df)

```

#Transforming SES
```{r}

#To measure standard of living, questions were asked about housing conditions, ownership of household appliances and access to transport. Composite standard of living scores will be created for each participant by taking the sum of all the items. For a composite SES, a sum of standardised responses to each of the 3 scales (standard of living, educational attainment and financial strain). 

#SoL composite (higher score = lower SoL)

# Code standard of living variable formed of the following categories:
# Housing comp: house tenure & type (2 items); overcrowding (1 item); quality of structural materials (3 items); household commodities (4 items); 
# Total electricals ownership (1 item); 
# Access to means of transport (1 item)

# HOUSING (9 items)


# ELECTRICALS OWNERSHIP (1 item); 0 = none; 6 = all six options
#var_label(df$el_count)
#table(df$el_count, useNA = "ifany")
df$rev_el_count <- 6-df$el_count 
#table(df$rev_el_count, useNA = "ifany")

# TRANSPORT; 0 = none avail; 1 = any avail
#table(tr_any, useNA = "ifany")
df$rev_tr_any <- ifelse(df$tr_any == 0, 1,
                    ifelse(df$tr_any == 1, 0, NA))
#table(df$rev_tr_any, useNA = "ifany")

# COMPOSITE SOL SCORE (higher = lower SoL)

df$miss_SoL<-apply(df[,c("tenure","hq1_housetype","hq2_roomsforsleep","hq3_floorqual","hq4_roofqual","hq5_wallqual","hq6_lighting","hq7_cookfuel","hq8_watersource","hq9_toilet", "rev_el_count","rev_tr_any")], MARGIN = 1, function(x) sum(is.na(x)))
table(df$miss_SoL)

df$SoL<-ifelse(df$miss_SoL > 1, NA, rowSums(df[,c("tenure","hq1_housetype","hq2_roomsforsleep","hq3_floorqual","hq4_roofqual","hq5_wallqual","hq6_lighting","hq7_cookfuel","hq8_watersource","hq9_toilet", "rev_el_count","rev_tr_any")], na.rm = TRUE))
table(df$SoL, useNA = "ifany")

# EDUCATION (recoded so higher score = lower)

#val_labels(df$education)
#table(df$education)
df$education <- ifelse(df$education > 5, NA, df$education)
df$rev_education <- 5-df$education
#table(df$rev_education, useNA = "ifany")

# FINANCIAL STRAIN

#val_labels(df$finstrain)
#table(df$finstrain, useNA = "ifany")

# STANDARDISE SES SUB-SCALES

df$stand_SoL <- as.vector(scale(df$SoL))

df$stand_rev_education <- as.vector(scale(df$rev_education))

df$stand_finstrain <-  as.vector(scale(df$finstrain))

df$SES <- df$stand_SoL + df$stand_rev_education + df$stand_finstrain

df$stand_SES <- as.vector(scale(df$SES)) #numeric data (continuous)

df$stand_SoL <- as.numeric(df$stand_SoL) #numeric data (continuous)
df$stand_rev_education<- as.numeric(df$stand_rev_education) #numeric data (continuous)
df$stand_finstrain<- as.numeric(df$stand_finstrain) #numeric data (continuous)

cvar <- df[,c("stand_SoL", "stand_rev_education", "stand_finstrain")]
(corrs <- round(cor(cvar, use = "p"),2))
```

# Transforming Affected by War

```{r}

df$affected.war <- df$c1_war1+df$c1_war2+df$c1_war3+df$c1_war4+df$c1_war5+df$c1_war6+df$c1_war7+df$c1_war8

#table(df$affected.war)

df$affected.war.bin[df$affected.war == 8] <- "0"
df$affected.war.bin[df$affected.war == 12] <- "1"
df$affected.war.bin[df$affected.war == 16] <- "1"
df$affected.war.bin[df$affected.war == 20] <- "1"
df$affected.war.bin[df$affected.war == 24] <- "1"
df$affected.war.bin[df$affected.war == 28] <- "1"

affected.war.bin <- df$affected.war.bin

table(affected.war.bin, useNA = "ifany") #logical data (binary ordinal)

```

# Transforming Affected by Tsunami

```{r}
df$affected.tsu <- tsu1 + tsu2 + tsu3 + tsu4 + tsu5 + tsu6 + tsu7 + tsu8 + tsu9

#table(df$affected.tsu)

df$affected.tsu.bin[df$affected.tsu == 9] <- "0"
df$affected.tsu.bin[df$affected.tsu == 13] <- "1"
df$affected.tsu.bin[df$affected.tsu == 17] <- "1"
df$affected.tsu.bin[df$affected.tsu == 21] <- "1"
df$affected.tsu.bin[df$affected.tsu == 25] <- "1"
df$affected.tsu.bin[df$affected.tsu == 29] <- "1"
df$affected.tsu.bin[df$affected.tsu == 33] <- "1"
df$affected.tsu.bin[df$affected.tsu == 37] <- "1"

affected.tsu.bin <- df$affected.tsu.bin

table(affected.tsu.bin, useNA = "ifany") #logical data (binary ordinal)

```

# Transforming Interpers Violence

```{r}

df$interpers_viol <- df$sle35_robbed + df$sle40_weapon + df$sle18_physabuse + df$sle42_sexabuse + df$sle43_scold_work + df$sle44_bullied + df$sle45_enthdisc +df$sle56_scam

df$interpers_viol <- as.numeric(df$interpers_viol)

table(df$interpers_viol, useNA = "ifany") #numeric integer data (continuous)

```

# Risk Factors for Violence - Poisson Regression 

```{r}

# Poisson Regression = suitable for count data such as integer data, number of interpersonal violence experiences

library(data.table)
library(arsenal)
library(lavaan)
library(lmtest)

Pois1 <- glm(formula = interpers_viol ~ sex, data = df, family=poisson)

summary(Pois1)
confint(Pois1)

#extract the incidence rate ratio
exp(coef(Pois1))
#extract the confidence intervals
exp(lmtest::coefci(Pois1))

Pois2 <- glm(formula = interpers_viol ~ stand_SES, data = df, family=poisson)

summary(Pois2)
confint(Pois2)

#extract the incidence rate ratio
exp(coef(Pois2))
#extract the confidence intervals
exp(lmtest::coefci(Pois2))

Pois3 <- glm(formula = interpers_viol ~ affected.tsu.bin, data = df, family=poisson)

summary(Pois3)
confint(Pois3)

#extract the incidence rate ratio
exp(coef(Pois3))
#extract the confidence intervals
exp(lmtest::coefci(Pois3))

Pois4 <- glm(formula = interpers_viol ~ affected.war.bin, data = df, family=poisson)

summary(Pois4)
confint(Pois4)

#extract the incidence rate ratio
exp(coef(Pois4))
#extract the confidence intervals
exp(lmtest::coefci(Pois4))

hist(df$age_yrs)

Pois5 <- glm(formula = interpers_viol ~ age_yrs, data = df, family=poisson)

summary(Pois5)
confint(Pois5)

#extract the incidence rate ratio
exp(coef(Pois5))
#extract the confidence intervals
exp(lmtest::coefci(Pois5))

#Sub-analysis in female participants

table(df$sex_c1c2)
femaledf <- subset(df, df$sex_c1c2 == 1)

Pois6 <- glm(formula = interpers_viol ~ stand_SES, data = femaledf, family=poisson)

summary(Pois6)
confint(Pois6)

#extract the incidence rate ratio
exp(coef(Pois6))
#extract the confidence intervals
exp(lmtest::coefci(Pois6))

Pois7 <- glm(formula = interpers_viol ~ affected.tsu.bin, data = femaledf, family=poisson)

summary(Pois7)
confint(Pois7)

#extract the incidence rate ratio
exp(coef(Pois7))
#extract the confidence intervals
exp(lmtest::coefci(Pois7))

Pois8 <- glm(formula = interpers_viol ~ affected.war.bin, data = femaledf, family=poisson)

summary(Pois8)
confint(Pois8)

#extract the incidence rate ratio
exp(coef(Pois8))
#extract the confidence intervals
exp(lmtest::coefci(Pois8))

Pois9 <- glm(formula = interpers_viol ~ age_yrs, data = femaledf, family=poisson)

summary(Pois9)
confint(Pois9)

#extract the incidence rate ratio
exp(coef(Pois9))
#extract the confidence intervals
exp(lmtest::coefci(Pois9))

#Sub-analysis in male participants

table(df$sex_c1c2)
maledf <- subset(df, df$sex_c1c2 == 0)

Pois10 <- glm(formula = interpers_viol ~ stand_SES, data = maledf, family=poisson)

summary(Pois10)
confint(Pois10)

#extract the incidence rate ratio
exp(coef(Pois10))
#extract the confidence intervals
exp(lmtest::coefci(Pois10))

Pois11 <- glm(formula = interpers_viol ~ affected.tsu.bin, data = maledf, family=poisson)

summary(Pois11)
confint(Pois11)

#extract the incidence rate ratio
exp(coef(Pois11))
#extract the confidence intervals
exp(lmtest::coefci(Pois11))

Pois12 <- glm(formula = interpers_viol ~ affected.war.bin, data = maledf, family=poisson)

summary(Pois12)
confint(Pois12)

#extract the incidence rate ratio
exp(coef(Pois12))
#extract the confidence intervals
exp(lmtest::coefci(Pois12))

Pois13 <- glm(formula = interpers_viol ~ age_yrs, data = maledf, family=poisson)

summary(Pois13)
confint(Pois13)

#extract the incidence rate ratio
exp(coef(Pois13))
#extract the confidence intervals
exp(lmtest::coefci(Pois13))
```

# Risk Factors for Violence - Cluster Poisson Regressions 

```{r}
m1 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ sex, cluster = "clustervar", family = "poisson")

summary(m1)

m2 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ stand_SES, cluster = "clustervar", family = "poisson")

summary(m2)

m3 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ affected.tsu.bin, cluster = "clustervar", family = "poisson")

summary(m3)

m4 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ affected.war.bin, cluster = "clustervar", family = "poisson")

summary(m4)

m5 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ age_yrs, cluster = "clustervar", family = "poisson")

summary(m5)

#Sub-analysis in female participants

m6 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ stand_SES, cluster = "clustervar", family = "poisson")

summary(m6)

m7 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ affected.tsu.bin, cluster = "clustervar", family = "poisson")

summary(m7)

m8 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ affected.war.bin, cluster = "clustervar", family = "poisson")

summary(m8)

m9 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ age_yrs, cluster = "clustervar", family = "poisson")

summary(m9)

#Sub-analysis in male participants

m10 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ stand_SES, cluster = "clustervar", family = "poisson")

summary(m10)

m11 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ affected.tsu.bin, cluster = "clustervar", family = "poisson")

summary(m11)

m12 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ affected.war.bin, cluster = "clustervar", family = "poisson")

summary(m12)

m13 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ age_yrs, cluster = "clustervar", family = "poisson")

summary(m13)

```

# Sex Diff in Means of IV scores
```{r}
table(df$sex_c1c2)

femaledf <- subset(df, df$sex_c1c2 == 1)
maledf <- subset(df, df$sex_c1c2 == 0)

summary(femaledf$interpers_viol)
summary(maledf$interpers_viol)
```

# Sex Diff in Each IV event
```{r}

# df$interpers_viol <- df$sle35_robbed + df$sle40_weapon + df$sle18_physabuse + df$sle42_sexabuse + df$sle43_scold_work + df$sle44_bullied + df$sle45_enthdisc +df$sle56_scam

#ROBERY 

table(df$sle35_robbed)
prop.table(table(df$sle35_robbed))

table(femaledf$sle35_robbed)
prop.table(table(femaledf$sle35_robbed))

table(maledf$sle35_robbed)
prop.table(table(maledf$sle35_robbed))

#WEAPON INJURY

table(df$sle40_weapon)
prop.table(table(df$sle40_weapon))

table(femaledf$sle40_weapon)
prop.table(table(femaledf$sle40_weapon))

table(maledf$sle40_weapon)
prop.table(table(maledf$sle40_weapon))

#PHYSICAL ABUSE

table(df$sle18_physabuse)
prop.table(table(df$sle18_physabuse))

table(femaledf$sle18_physabuse)
prop.table(table(femaledf$sle18_physabuse))

table(maledf$sle18_physabuse)
prop.table(table(maledf$sle18_physabuse))

#SEXUAL ABUSE

table(df$sle42_sexabuse)
prop.table(table(df$sle42_sexabuse))

table(femaledf$sle42_sexabuse)
prop.table(table(femaledf$sle42_sexabuse))

table(maledf$sle42_sexabuse)
prop.table(table(maledf$sle42_sexabuse))

#SCOLDING AT WORK

table(df$sle43_scold_work)
prop.table(table(df$sle43_scold_work))

table(femaledf$sle43_scold_work)
prop.table(table(femaledf$sle43_scold_work))

table(maledf$sle43_scold_work)
prop.table(table(maledf$sle43_scold_work))

#BULLYING

table(df$sle44_bullied)
prop.table(table(df$sle44_bullied))

table(femaledf$sle44_bullied)
prop.table(table(femaledf$sle44_bullied))

table(maledf$sle44_bullied)
prop.table(table(maledf$sle44_bullied))

#ETHNIC DISC

table(df$sle45_enthdisc)
prop.table(table(df$sle45_enthdisc))

table(femaledf$sle45_enthdisc)
prop.table(table(femaledf$sle45_enthdisc))

table(maledf$sle45_enthdisc)
prop.table(table(maledf$sle45_enthdisc))

#SCAMMED

table(df$sle56_scam)
prop.table(table(df$sle56_scam))

table(femaledf$sle56_scam)
prop.table(table(femaledf$sle56_scam))

table(maledf$sle56_scam)
prop.table(table(maledf$sle56_scam))

#LOG REGRESSION 

#robbery 

logreg1 <- miceadds::glm.cluster(data = df, formula = df$sle35_robbed ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg1)
confint(logreg1)
exp(cbind("Odds ratio" = coef(logreg1), confint.default(logreg1, level = 0.95)))

#weapon

logreg2 <- miceadds::glm.cluster(data = df, formula = df$sle40_weapon ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg2)
confint(logreg2)
exp(cbind("Odds ratio" = coef(logreg2), confint.default(logreg2, level = 0.95)))

#physical abuse 

logreg3 <- miceadds::glm.cluster(data = df, formula = df$sle18_physabuse ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg3)
confint(logreg3)
exp(cbind("Odds ratio" = coef(logreg3), confint.default(logreg3, level = 0.95)))

#sexual abuse 

logreg4 <- miceadds::glm.cluster(data = df, formula = df$sle42_sexabuse ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg4)
confint(logreg4)
exp(cbind("Odds ratio" = coef(logreg4), confint.default(logreg4, level = 0.95)))

#scoulded

logreg5 <- miceadds::glm.cluster(data = df, formula = df$sle43_scold_work ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg5)
confint(logreg5)
exp(cbind("Odds ratio" = coef(logreg5), confint.default(logreg5, level = 0.95)))

#bullying 

logreg6 <- miceadds::glm.cluster(data = df, formula = df$sle44_bullied ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg6)
confint(logreg6)
exp(cbind("Odds ratio" = coef(logreg6), confint.default(logreg6, level = 0.95)))

#ethnic discrimination

logreg7 <- miceadds::glm.cluster(data = df, formula = df$sle45_enthdisc ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg7)
confint(logreg7)
exp(cbind("Odds ratio" = coef(logreg7), confint.default(logreg7, level = 0.95)))

#scam 

logreg8 <- miceadds::glm.cluster(data = df, formula = df$sle56_scam ~ sex, cluster = "clustervar", family = "binomial")

summary(logreg8)
confint(logreg8)
exp(cbind("Odds ratio" = coef(logreg8), confint.default(logreg8, level = 0.95)))

```

# Risk Factors for Violence - Cluster Linear Regressions 

```{r}
lin1 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ sex, cluster = "clustervar")

summary(lin1)
confint(lin1)

sum(!is.na(df$interpers_viol)&!is.na(df$sex_c1c2))
sum(is.na(df$interpers_viol)&!is.na(df$sex_c1c2)) #39

lin2 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ stand_SES, cluster = "clustervar")

summary(lin2)
confint(lin2)

# Missing Data Amount
sum(!is.na(df$interpers_viol)&!is.na(df$stand_SES))
sum(!is.na(df$interpers_viol)&is.na(df$stand_SES)) #20
sum(is.na(df$interpers_viol)&!is.na(df$stand_SES)) #6 = 26 total

lin3 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ affected.tsu.bin, cluster = "clustervar")

summary(lin3)
confint(lin3)

# Missing Data Amount
sum(!is.na(df$interpers_viol)&!is.na(df$affected.tsu.bin))
sum(!is.na(df$interpers_viol)&is.na(df$affected.tsu.bin)) #9
sum(is.na(df$interpers_viol)&!is.na(df$affected.tsu.bin)) #39 total = 48

lin4 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ affected.war.bin, cluster = "clustervar")

summary(lin4)
confint(lin4)

# Missing Data Amount
sum(!is.na(df$interpers_viol)&!is.na(df$affected.war.bin))
sum(!is.na(df$interpers_viol)&is.na(df$affected.war.bin)) #6
sum(is.na(df$interpers_viol)&!is.na(df$affected.war.bin)) #39 total = 45

lin5 <- miceadds::glm.cluster(data = df, formula = interpers_viol ~ age_yrs, cluster = "clustervar")

summary(lin5)
confint(lin5)

# Missing Data Amount
sum(!is.na(df$interpers_viol)&!is.na(df$age_yrs))
sum(!is.na(df$interpers_viol)&is.na(df$age_yrs)) #0
sum(is.na(df$interpers_viol)&!is.na(df$age_yrs)) #6 total = 6

#Sub-analysis in female participants

lin6 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ stand_SES, cluster = "clustervar")

summary(lin6)
confint(lin6)

lin7 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ affected.tsu.bin, cluster = "clustervar")

summary(lin7)
confint(lin7)

lin8 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ affected.war.bin, cluster = "clustervar")

summary(lin8)
confint(lin8)

lin9 <- miceadds::glm.cluster(data = femaledf, formula = interpers_viol ~ age_yrs, cluster = "clustervar")

summary(lin9)
confint(lin9)

#Sub-analysis in male participants

lin10 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ stand_SES, cluster = "clustervar")

summary(lin10)
confint(lin10)

lin11 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ affected.tsu.bin, cluster = "clustervar")

summary(lin11)
confint(lin11)

lin12 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ affected.war.bin, cluster = "clustervar")

summary(lin12)
confint(lin12)

lin13 <- miceadds::glm.cluster(data = maledf, formula = interpers_viol ~ age_yrs, cluster = "clustervar")

summary(lin13)
confint(lin13)

```

# IV by age

```{r}

df$age_cat <- ifelse(df$age_yrs > 18 & df$age_yrs < 30, 1,
                     ifelse(df$age_yrs > 29 & df$age_yrs < 40, 2,
                            ifelse(df$age_yrs > 39 & df$age_yrs < 50, 3,
                                   ifelse(df$age_yrs > 49 & df$age_yrs < 60, 4,
                                          ifelse(df$age_yrs > 59 & df$age_yrs < 70, 5,
                                                 ifelse(df$age_yrs > 69, 6, NA))))))

df$age_cat <- as.factor(df$age_cat)

table(df$age_cat, df$interpers_viol)

hist(df$interpers_viol)
summary(df$age_cat)

df %>%
  group_by(age_cat) %>%
  summarise_at(vars(interpers_viol), list(name = mean), na.rm=TRUE)

```


