---
title: "Bivariate GxE: Depression moderated by interpersonal violence  (COTASS)"
author: "Filip Kaleta"
date: "2024-02-20"
output: 
  html_document:
    toc: true
---

# Load packages  
```{r include=FALSE}

rm(list=ls())

# Packages

require(OpenMx)
require(Hmisc)
require(psych)
require(plyr)
library(haven)
require(psych)
library(dplyr)
library(tidyverse)
library(labelled)

```

# Prep data
```{r}

df <- read_dta("IPV-and-depression3.dta") #N = 5961

df <- df[!(df$whichcotass == 1 | df$whichcotass == 2),] #Only keeping participants with COTASS 1 and COTASS 2 data (most vars and analyses are T2 anyway, so creates a lot of NA id we keep T1) N = 3876

df$interpers_viol <- df$sle35_robbed + df$sle40_weapon + df$sle18_physabuse + df$sle42_sexabuse + df$sle43_scold_work + df$sle44_bullied + df$sle45_enthdisc + df$sle56_scam

df$interpers_viol <- as.numeric(df$interpers_viol) 

dtw <- df[c("numclust", "c1c2_sexzyg", "numtw_noDZOS", "sing_or_twin", "sex_c1c2",  "age_yrs","interpers_viol", "pbecktot")]

dtw<-data.frame(dtw) 

head(dtw)

## Need to recode numtw_noDZOS so that singletons are given put in 'twin 1'
table(dtw$numtw_noDZOS, useNA = "ifany")
table(dtw$sing_or_twin)

dtw$TwNo <- ifelse(is.na(dtw$numtw_noDZOS), 1, 
                           ifelse(dtw$numtw_noDZOS == 1, 1,
                                  ifelse(dtw$numtw_noDZOS == 2, 2, 
                                         ifelse(dtw$numtw_noDZOS == 3, 3, NA))))
table(dtw$TwNo, useNA = "ifany")

# Because we don't want triplets, remove lines in which TwNo==3; this removes the 3rd sibling in each triplet group
table(dtw$c1c2_sexzyg, useNA = "ifany")
which(is.na(dtw$c1c2_sexzyg))
dtw <- dtw[!(dtw$c1c2_sexzyg == 7),]
dtw <- dtw[!is.na(dtw$c1c2_sexzyg),]

table(dtw$TwNo, useNA = "ifany")


psych::describe(dtw)
head(dtw)

# Delete unnecessary vars & rename variables in sub data to make it easier. 

dtw <- dtw[c("numclust", "c1c2_sexzyg", "sing_or_twin", "sex_c1c2", "age_yrs","interpers_viol", "pbecktot", "TwNo")]

names(dtw) <- c("FamID", "sexzyg", "sing_or_twin", "sex", "age", "interpers_viol", "bdi_dep", "TwNo")
```

# Remove outliers, regress out covariates, transform, reshape (if necessary)

```{r}
#Depression

## BDI Depression Log Transformations

sum(is.na(dtw$bdi_dep)) #51
hist(dtw$bdi_dep)
psych::describe(dtw$bdi_dep)

dtw$bdi_dep_resid <- residuals(lm(dtw$bdi_dep ~ dtw$sex + dtw$age, na.action="na.exclude"))
sum(is.na(dtw$bdi_dep_resid)) #51
hist(dtw$bdi_dep_resid)
psych::describe(dtw$bdi_dep_resid)

# Log transformation + standardise

dtw$bdi_depT <- log(dtw$bdi_dep_resid + 8)*2
hist(dtw$bdi_depT)
psych::describe(dtw$bdi_depT) 

dtw$bdi_depTS <- scale(dtw$bdi_depT)
hist(dtw$bdi_depTS)
psych::describe(dtw$bdi_depTS)
sum(is.na(dtw$bdi_depTS)) #

# No logT 
#dtw$bdi_dep_rS <- scale(dtw$bdi_dep_resid)
#psych::describe(dtw$bdi_dep_rS)
#hist(dtw$bdi_dep_rS)

## Interpers Viol Log Transformations

sum(is.na(dtw$interpers_viol)) #38
dtw$interpers_viol <- as.numeric(dtw$interpers_viol)
hist(dtw$interpers_viol)
psych::describe(dtw$interpers_viol)

dtw$interpers_viol_resid <- residuals(lm(dtw$interpers_viol ~ dtw$sex + dtw$age, na.action="na.exclude"))
sum(is.na(dtw$interpers_viol_resid)) #38
hist(dtw$interpers_viol_resid)
psych::describe(dtw$interpers_viol_resid)

# Log transformation

dtw$interpers_violT <- log(dtw$interpers_viol_resid + 1)*2
hist(dtw$interpers_violT)
psych::describe(dtw$interpers_violT)

dtw$interpers_violTS <- scale(dtw$interpers_violT)
hist(dtw$interpers_violTS)
psych::describe(dtw$interpers_violTS)
sum(is.na(dtw$interpers_violTS)) #38

```

# Reshape data from long format to wide format for twin analysis:
```{r include=FALSE}

dtw 	<- reshape(dtw, idvar = c("FamID","sexzyg"), timevar = "TwNo", direction = "wide", sep = "")

# Check data
str(dtw)
psych::describe(dtw)

```

# Create data groups 
```{r "create data groups", include = T, echo = T, collapse = T, eval = T}

## Prepare data

# Create new variable to be used as definition variable (i.e. moderator)
dtw$interpers_violm1 <- dtw$interpers_violTS1
dtw$interpers_violm2 <- dtw$interpers_violTS2
#describe(dtw$interpers_violm1)
#describe(dtw$interpers_violm2)

nv <- 2		# number of variables per twin
ntv <- nv*2	# number of variables per pair

# Select Variables for Analysis
Vars <- c('interpers_violTS','bdi_depTS')
selVars <- paste(Vars,c(rep(1,nv),rep(2,nv)),sep="")
selVarsS <- c('interpers_violTS1','bdi_depTS1')
defVars <- c('interpers_violm1','interpers_violm2')

# Drop cases with missingness on the definition variables

mzData <-dtw[c(dtw$sexzyg==1 | dtw$sexzyg==3) & !is.na(dtw$interpers_violTS1) & !is.na(dtw$interpers_violTS2), c(selVars, c('interpers_violm1','interpers_violm2'))]
dzData <-dtw[c(dtw$sexzyg==2 | dtw$sexzyg==4 | dtw$sexzyg == 5) & !is.na(dtw$interpers_violTS1) & !is.na(dtw$interpers_violTS2), c(selVars, c('interpers_violm1','interpers_violm2'))]
sData <-dtw[dtw$sexzyg==6 & !is.na(dtw$interpers_violTS1), c(selVarsS, 'interpers_violm1')]

#describe(mzData)
#describe(dzData)
#describe(sData)

```

# Generate descriptive statistics

```{r "descriptives", include = T, echo = T, collapse = T, eval = T}

colMeans(mzData,na.rm=TRUE)
colMeans(dzData,na.rm=TRUE)
colMeans(sData,na.rm=TRUE)

cov(mzData,use="complete")
cov(dzData,use="complete")
cov(sData,use="complete")

cor(mzData,use="complete")
cor(dzData,use="complete")
cor(sData,use="complete")

sqrt(cov(mzData, use="complete")/5)
sqrt(cov(dzData, use="complete")/5)
sqrt(cov(sData, use="complete")/5)

```

# Script for bivariate GxE model 
```{r "run GxE model - v1", include = T, echo = T, eval = T}

# PREPARE MODEL -----------------------------------------------------------

# Matrix for expected Means

meanG     <- mxMatrix(type="Full", nrow=1, ncol=ntv, free=TRUE, values=.01, label=c("m1","m2","m1","m2"), name="expMean") #m1 = SoL; m2 = depression (need both means for the objective objects for multiple groups (line 188) code to work)
meanS <- mxMatrix(type = "Full", nrow=1, ncol=2, free=TRUE, values=.01, label=c("m1","m2"), name="expMeanS") # singletons 

# Matrices declared to store a, c, and e Path Coefficients
pathA     <- mxMatrix(type="Lower", nrow=nv, ncol=nv, free=TRUE, values=.6, label=c("a11","a21","a22"), name="a") 
pathC     <- mxMatrix(type="Lower", nrow=nv, ncol=nv, free=TRUE, values=.6, label=c("c11","c21","c22"), name="c") 
pathE     <- mxMatrix(type="Lower", nrow=nv, ncol=nv, free=TRUE, values=.6, label=c("e11","e21","e22"), name="e") 

# Matrices generated to hold A, C, and E computed Variance Components
covA      <- mxAlgebra(expression=a %*% t(a), name="A")
covC      <- mxAlgebra(expression=c %*% t(c), name="C") 
covE      <- mxAlgebra(expression=e %*% t(e), name="E")

# Algebra to compute total variances and standard deviations (diagonal only)
covP      <- mxAlgebra(expression=A+C+E, name="V")
matI      <- mxMatrix(type="Iden", nrow=nv, ncol=nv, name="I")
invSD     <- mxAlgebra(expression=solve(sqrt(I*V)), name="iSD")

# Algebras generated to create summary Table of Derived Variance Components
rowVars   <- rep('vars',nv)
colVars   <- rep(c('A','C','E','SA','SC','SE'),each=nv)
estVars   <- mxAlgebra(expression=cbind(A,C,E,A/V,C/V,E/V), name="Vars", dimnames=list(rowVars,colVars))

# Matrix for moderating/interacting variable
definterpers_violm1   <- mxMatrix(type="Full", nrow=1, ncol=1, free=FALSE, labels=c("data.interpers_violm1"), name="interpers_violm1")
definterpers_violm2   <- mxMatrix(type="Full", nrow=1, ncol=1, free=FALSE, labels=c("data.interpers_violm2"), name="interpers_violm2")

# Matrices declared to store moderated a, c, and e Path Coefficients
pathAm    <- mxMatrix(type="Lower", nrow=nv, ncol=nv, free=c(F,T,T), values=c(0,.01,.01), label=c("fix","am21","am22"), name="aMod") 
pathCm    <- mxMatrix(type="Lower", nrow=nv, ncol=nv, free=c(F,T,T), values=c(0,.01,.01), label=c("fix","cm21","cm22"), name="cMod")
pathEm    <- mxMatrix(type="Lower", nrow=nv, ncol=nv, free=c(F,T,T), values=c(0,.01,.01), label=c("fix","em21","em22"), name="eMod")

# Matrices generated to hold moderated A, C, and E computed Variance Components
varAm1    <- mxAlgebra(expression=(a+ interpers_violm1%x%aMod) %*% t(a+ interpers_violm1%x%aMod), name="Am1")
varCm1    <- mxAlgebra(expression=(c+ interpers_violm1%x%cMod) %*% t(c+ interpers_violm1%x%cMod), name="Cm1")
varEm1    <- mxAlgebra(expression=(e+ interpers_violm1%x%eMod) %*% t(e+ interpers_violm1%x%eMod), name="Em1")

varAm2    <- mxAlgebra(expression=(a+ interpers_violm2%x%aMod) %*% t(a+ interpers_violm2%x%aMod), name="Am2")
varCm2    <- mxAlgebra(expression=(c+ interpers_violm2%x%cMod) %*% t(c+ interpers_violm2%x%cMod), name="Cm2")
varEm2    <- mxAlgebra(expression=(e+ interpers_violm2%x%eMod) %*% t(e+ interpers_violm2%x%eMod), name="Em2")

covAm12   <- mxAlgebra(expression=(a+ interpers_violm1%x%aMod) %*% t(a+ interpers_violm2%x%aMod), name="Am12")
covCm12   <- mxAlgebra(expression=(c+ interpers_violm1%x%cMod) %*% t(c+ interpers_violm2%x%cMod), name="Cm12")
covAm21   <- mxAlgebra(expression=(a+ interpers_violm2%x%aMod) %*% t(a+ interpers_violm1%x%aMod), name="Am21")
covCm21   <- mxAlgebra(expression=(c+ interpers_violm2%x%cMod) %*% t(c+ interpers_violm1%x%cMod), name="Cm21")

# Algebra to compute total variances and standard deviations (diagonal only)
covPm1    <- mxAlgebra(expression=Am1+Cm1+Em1, name="Vm1")
covPm2    <- mxAlgebra(expression=Am2+Cm2+Em2, name="Vm2")

# Algebra for expected Mean and Variance/Covariance Matrices in MZ & DZ twins
covMZ    <- mxAlgebra(expression= rbind(cbind(Vm1, Am12+Cm12), cbind(Am21+Cm21, Vm2)), name="expCovMZ")
covDZ    <- mxAlgebra(expression= rbind(cbind(Vm1, 0.5%x%Am12+Cm12), cbind(0.5%x%Am21+Cm21, Vm2)), name="expCovDZ")

# Algebra to derive expected variance singletons
covS		<-mxAlgebra(((a+aMod*interpers_violm1)*t(a+aMod*interpers_violm1)) + ((c+cMod*interpers_violm1)*t(c+cMod*interpers_violm1)) + ((e+eMod*interpers_violm1)*t(e+eMod*interpers_violm1)), name="Vm1") # singletons 

# Data objects for Multiple Groups
dataMZ <-mxData(observed=mzData, type="raw")
dataDZ <-mxData(observed=dzData, type="raw")
dataS	<-mxData(observed=sData, type="raw")

# Objective objects for Multiple Groups
objMZ  <- mxExpectationNormal(covariance="expCovMZ", means="expMean", dimnames=selVars)
objDZ  <- mxExpectationNormal(covariance="expCovDZ", means="expMean", dimnames=selVars)
objS		<- mxExpectationNormal(covariance="Vm1", means="expMeanS", dimnames=selVarsS) # singletons 

funML <- mxFitFunctionML()

# Combine Groups

pars    <- list(pathA, pathC, pathE, pathAm, pathCm, pathEm, meanG, meanS, covA, covC, covE, covP, matI, invSD, estVars)
defs    <- list(definterpers_violm1, definterpers_violm2, varAm1, varCm1, varEm1, covPm1, varAm2, varCm2, varEm2, covPm2, covAm12, covCm12, covAm21, covCm21)
modelMZ <- mxModel(pars, defs, covMZ, dataMZ, objMZ, funML, name="MZ")
modelDZ <- mxModel(pars, defs, covDZ, dataDZ, objDZ, funML, name="DZ")
modelSs	<- mxModel(pars, definterpers_violm1, varAm1, varCm1, varEm1, covPm1, covS, dataS, objS, funML,name="Ss") #singletons   
multi <- mxFitFunctionMultigroup(c("MZ","DZ","Ss"))
ci <-mxCI(c('MZ.a', 'MZ.c', 'MZ.e')) 
cim <-mxCI(c('MZ.aMod', 'MZ.cMod', 'MZ.eMod')) 	
ModAceModel <- mxModel("ModACE", pars, modelMZ, modelDZ, modelSs, ci, cim, multi)

```

# Run bix GxE Model
```{r}

#ModAceFit <- mxRun(ModAceModel, intervals =T)
ModAceFit <- mxTryHard(ModAceModel, intervals = T, extraTries = 20)
(ModAceSum <- summary(ModAceFit))

#ModAceSum$parameters
round(ModAceFit@output$estimate,4)
round(ModAceFit$Vars@result,4)

```

# Submodel 1 - drop all moderators 
```{r "submodels-1", include = T, echo = T, eval = T}

NoModModel<-mxModel(ModAceFit, name="NoMod")
NoModModel<-omxSetParameters(NoModModel, labels=c("am21","am22","cm21","cm22","em21","em22"), free=F, values=0)
NoModFit <-mxTryHard(NoModModel, intervals=T)
(NoModSumm <-summary(NoModFit))

mxCompare(ModAceFit,NoModFit)

```

# Sub model 2 - drop a22, c22 and e22 
```{r "submodels-2", include = T, echo = T, eval = T}

subMod2<-mxModel(ModAceFit, name="subMod2")
subMod2<-omxSetParameters(subMod2, labels=c("am22","cm22","em22"), free=F, values=0)
subMod2Fit <-mxTryHard(subMod2, intervals=T)
(subMod2Summ <-summary(subMod2Fit))

mxCompare(ModAceFit,subMod2Fit)

```

# Sub model 3 - drop a21, c21 and e21
```{r}

subMod3<-mxModel(ModAceFit, name="subMod3")
subMod3<-omxSetParameters(subMod3, labels=c("am21","cm21","em21"), free=F, values=0)
subMod3Fit <-mxTryHard(subMod3, intervals=T)
(subMod3Summ <-summary(subMod3Fit))

mxCompare(ModAceFit,subMod3Fit)

```

# Compare all models
```{r "nest-fit", include = T, echo = T, eval = T}

(Nested.fit <- 	rbind	(
			mxCompare(ModAceFit, NoModFit) [1,],
			mxCompare(ModAceFit, NoModFit) [2,],
			mxCompare(ModAceFit, subMod2Fit) [2,],
			mxCompare(ModAceFit, subMod3Fit) [2,]))

mxCompare(ModAceFit, NoModFit)
mxCompare(ModAceFit, subMod2Fit)
mxCompare(subMod2Fit, NoModFit)

```

# Plot interaction effects 
```{r "plot interactions"}

## Assign estimated parameters to variables

# path estimates
a11	<- ModAceFit$a[1,1]@values
a21 <- ModAceFit$a[2,1]@values
a22 <- ModAceFit$a[2,2]@values
c11	<- ModAceFit$c[1,1]@values
c21 <- ModAceFit$c[2,1]@values
c22 <- ModAceFit$c[2,2]@values
e11	<- ModAceFit$e[1,1]@values
e21 <- ModAceFit$e[2,1]@values
e22 <- ModAceFit$e[2,2]@values

# moderator terms 
am21 <- ModAceFit$aMod[2,1]@values
am22 <- ModAceFit$aMod[2,2]@values
cm21 <- ModAceFit$cMod[2,1]@values
cm22 <- ModAceFit$cMod[2,2]@values
em21 <- ModAceFit$eMod[2,1]@values
em22 <- ModAceFit$eMod[2,2]@values

## Sort moderator values and save to vector
modVal <- sort(unique(c(dtw$interpers_violm1,dtw$interpers_violm2)))

Vam21 <- ((c(a21)+(c(modVal)*c(am21)))^2)
Vam22 <- ((c(a22)+(c(modVal)*c(am22)))^2)
Vcm21 <- ((c(c21)+(c(modVal)*c(cm21)))^2)
Vcm22 <- ((c(c22)+(c(modVal)*c(cm22)))^2)
Vem21 <- ((c(e21)+(c(modVal)*c(em21)))^2)
Vem22 <- ((c(e22)+(c(modVal)*c(em22)))^2)

#Vacov <-2* (0.5 * c(am) * (c(ap)+(c(modVal)*c(m_ap))) * (c(p)+(c(modVal)*c(m_p)))) # example from GxE MCoTS model
#Vccov <-2* (c(cp)+(c(modVal)*c(m_cp)) * (c(p)+(c(modVal)*c(m_p))))

Vacov <- 2*(c(a21)+(c(modVal)*c(am21)))
Vccov <- 2*(c(c21)+(c(modVal)*c(cm21)))

#Vt <- Vam21 + Vam22 + Vcm21 + Vcm22 + Vem21 + Vem22 
#Vt <- Vam22 + Vam21 + Vcm22 + Vcm21 + Vem22 + Vem21 
Vt <- Vam22 + Vam21 + Vcm22 + Vcm21 + Vem22 + Vem21 + Vacov + Vccov

#varcomps <- as.matrix(cbind(Vam21,Vam22,Vcm21,Vcm22,Vem21,Vem22,Vt))
varcomps <- as.matrix(cbind(Vam22,Vam21,Vcm22,Vcm21,Vem22,Vem21,Vt))
head(varcomps)

# Plot variance components as a function of the moderator
# NB: Va = red, Vc = orange, Ve = blue, VaC = purple, VcC = yellow, VeC = green, Vt = black
# NB: Va = red, VaC = orange, Vc = blue, VcC = purple, Ve = green, VeC = yellow, Vt = black

matplot(
  modVal,
  varcomps,
  type="l",
  lwd=2,
  lty=1,
  las=1,
  ylim=c(0,3),
  #col=c("red","orange","blue","purple","yellow","green","black"),
  col=c("red","orange","blue","purple","green","yellow","black"),
  frame=FALSE,
  main="Bivariate moderation of variance components: Depression Symptoms",
  xlab="Moderator: Interpersonal Violence",
  ylab="Variance Components"
  
)
#legend("topright",legend=c("Au","Ac","Cu","Cc","Eu","Ec","Total variance"),col=c("red","orange","blue","purple","green","yellow","black"),lty=1)


```

```{r "plot interactions 2"}

varcomps1 <- as.matrix(cbind(Vam22,Vcm22,Vem22,Vt))
head(varcomps1)

matplot(
  modVal,
  varcomps1,
  type="l",
  lwd=2,
  lty=1,
  las=1,
  ylim=c(0,2),
  col=c("red","blue","green","black"),
  frame=FALSE,
  main="Bivariate moderation of variance components: Depression Symptoms",
  xlab="Moderator (Interpersonal Violence)",
  ylab="Variance Components"
  
)
legend("topright",legend=c("A22","C22","E22","Total variance"),col=c("red","blue","green","black"),lty=1)

varcomps2 <- as.matrix(cbind(Vam21,Vcm21,Vem21,Vt))
head(varcomps2)

matplot(
  modVal,
  varcomps2,
  type="l",
  lwd=2,
  lty=1,
  las=1,
  ylim=c(0,2),
  col=c("orange","purple","yellow","black"),
  frame=FALSE,
  main="Bivariate moderation of variance components: Depression Symptoms",
  xlab="Moderator (Interpersonal Violence)",
  ylab="Variance Components"
  
)
legend("topright",legend=c("A21","C21","E21","Total variance"),col=c("orange","purple","yellow","black"),lty=1)

```
